Creating optimal conditions for reproducible data analysis in \R with `fertile'\protect\thanks{The authors gratefully acknowledge contributions from Hadley Wickham, Jenny Bryan, Greg Wilson, Edgar Ruiz, and other members of the \pkg{tidyverse} team.}

### 2020-07-17 STAT-paper-template/APA/fertile.Rnw
wording changes in intro

Much of the discussion around reproducibility is also generalized, written to be applicable to users working with a variety of statistical software programs. Since all statistical software programs operate differently, generalized recommendations on reproducibility are often shallow and unspecific. While they provide useful guidelines, they can often be difficult to implement, particularly to new analysts who are unsure how to apply such recommendations within the software programs they are using. Thus, reproducibility recommendations tailored to specific software programs are more likely to be adopted.

In this paper, we focus on reproducibility in the \R programming language with a concentration on projects that use the RStudio integrated development environment. \R is an ideal candidate for reproducibility recommendations due to the language's popularity for statistical analyses and the ease with which analysts can download and begin using the software.

A small body of papers and \R packages focusing on reproducibility in the \R community have been published. Much of this work is narrowly tailored, with each package effectively addressising a small component of reproducibility: file structure, modularization of code, version control, etc. Many existing reproducibility packages, due to their focused nature, succeed at their area of focus, but at a cost. They are often difficult to learn and operate, providing a barrier to entry for less-experienced data analysts. This can make the goal of achieving reproducibility unnecessarily challenging, leading to users becoming discouraged and deciding that the effort necessary to succeed is not worth it.

A much more effective way to achieve widespread reproducibility is to make the process for doing so simple enough so that it takes next to no conscious effort to implement. However, there appear to be no existing tools that fit this model--catering to analysts looking for an easy-to-learn, easy-to-implement, fast, way to obtain a broad overview of their projects' reproducibility. To address this, we present an \R package called \pkg{fertile}, a low barrier-to-entry package which focuses on a series of common mistakes programmers make while conducting data science research in R.

@@

Reproducibility is critically important to the advancement of knowledge in all fields of scientific research. Researchers are acknowledging this; publications and discussions focusing on reproducibility seem to have increased in frequency over the last several years (\cite{sep-scientific-reproducibility}, \cite{plos-biology}, \cite{bioessays-gosselin}, \cite{eisner-reproducibility}, \cite{engineering-reproducibility}).

Much of the available literature is focused on methods for achieving reproducibility in specific disciplines, and some of their recommendations are generalizable to all areas of scientific research. There is also work focusing specifically on reproducibility within the \R community. Some of this work is in the form of academic papers, while other literature comes from blog posts, websites, and \R packages, some of which are compiled by notable R-focused developers and researchers. In this section, we will discuss the reproducibility recommendations from both the formal and informal publications, which together influence the development of \pkg{fertile}.

@@

\cite{cooper2017guide} focuses on data analysis in \R and identifies similar important reproducibility components, while reiterating the need for clearly labeled, well-documented, and well-separated files. In addition, they recommend publishing a list of dependencies and using version control.

>>>>

Much of the discussion around reproducibility is also generalized, written to be applicable to users working with a variety of statistical software programs. Because all statistical software programs operate differently, generalized recommendations regarding reproducibility are often shallow and vague. While they provide useful guidelines, they can often be difficult to implement, particularly to new analysts who are unsure of how to apply such recommendations within the software programs they are using. Thus, reproducibility recommendations tailored to specific software programs are more likely to be adopted.

In this paper, we focus on reproducibility in the \R programming language, concentrating specifically on projects that use the RStudio integrated development environment. \R is an ideal candidate for reproducibility recommendations because of its accessibility and popularity as a tool for statistical analysis.

A small body of \R packages which focus on reproducibility have been published in recent years. Much of this work is narrowly tailored, with each package effectively addressing a small component of reproducibility: file structure, modularization of code, version control, etc. These packages often  succeed in their area of focus, but at the cost of accessibility to a wider audience. They are often difficult to learn and operate, providing a barrier to entry for less-experienced data analysts. This can lead users to become discouraged and abandon attempts to achieve reproducibility.

A much more effective way of realizing widespread reproducibility is to make the process for doing so simple enough that it takes little to no conscious effort to implement. However, there appear to be no existing tools that fit this model--catering to analysts looking for a simple, easy-to-implement, and fast way to obtain a broad overview of their projects' reproducibility. To address this, we present \pkg{fertile}, a low barrier-to-entry package focusing on common mistakes programmers make while conducting data science research in R.

@@

Reproducibility is essential to the advancement of knowledge in all fields of scientific research. Researchers acknowledge this; publications and discussions focusing on reproducibility appear to have increased in frequency over the last several years (\cite{sep-scientific-reproducibility}, \cite{plos-biology}, \cite{bioessays-gosselin}, \cite{eisner-reproducibility}, \cite{engineering-reproducibility}).

Much of the available literature is focused on methods for achieving reproducibility in specific disciplines and some of their recommendations are generalizable to all areas of scientific research. There is also work focusing specifically on reproducibility within the \R community. Some of this work is in the form of academic papers, while other literature comes from blog posts, websites, and \R packages, some of which are compiled by notable R-focused developers and researchers. In this section, we will discuss the reproducibility recommendations from both the formal and informal publications, which together have influenced the development of \pkg{fertile}.

@@

\cite{cooper2017guide} focuses on data analysis in \R and identifies a similar list of important reproducibility components and reiterates the need for clearly labeled, well-documented, and well-separated files. In addition, they recommend publishing a list of dependencies and using version control.
